Figures for conference paper

### 2019-06-05 Conference/EDM2019/conference figures EDM2019.Rmd
relocate script for conference figures into folder of conference

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())

@@

output_folder <- "Conference/Figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

@@

# Save by hand
# image format: JPEG
# Width: 626
# Check Maintain aspect ratio
# File name: Conference/Figures/Flowchart
```

>>>>

# TODO: set working directory to project directory
setwd("C:/Users/JeanLuc/Desktop/Job/DARS/DARS")

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())
knitr::opts_chunk$set(fig.path = "Figures/")

@@

output_folder <- "Figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

@@

# Save by hand
# File name: Conference/Figures/Flowchart
```
